\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{hyphenat}
\usepackage{fontawesome}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeEducationHeading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeOrganizationHeading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textit{\small #2} \\
      \textit{\small#3}
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    \textbf{\Huge \scshape Andrew Bruce} \\ \vspace{3pt}
    \small
    \faMobile \hspace{.5pt} \href{tel:14082073992}{+1(408)207-3992}
    $|$
    \faAt \hspace{.5pt} \href{mailto:andy@andycbruce.com}{andy@andycbruce.com}
    $|$
    \faLinkedinSquare \hspace{.5pt} \href{https://www.linkedin.com/in/andy-bruce-7154b920b/}{LinkedIn}
    $|$
    \faGithub \hspace{.5pt} \href{https://github.com/andychenbruce}{GitHub}
    $|$
    \faGlobe \hspace{.5pt} \href{https://andycbruce.com}{Portfolio}
\end{center}

\section{Experience}
  \vspace{3pt}
  \resumeSubHeadingListStart

    \resumeSubheading
      {University of California}{Santa Cruz, CA}
      {Graduate Researcher, Teaching Assistant}{Dec 2023 \textbf{--} Present}
        \resumeItemListStart
            \resumeItem{Ported OpenMM, a molecular dynamics simulation library used by thousands of scientists, to run with 16-bit floating point precision CUDA increasing simulation speed.}
            \resumeItem{Designed and trained graph neural networks for predicting the energy surface of coarse-grained proteins, massively speeding up the simulation of protein interactions.}
            \resumeItem{Implemented sharding algorithms for running simulations over hundreds of A100 GPUs in multiple compute clusters}
        \resumeItemListEnd

    \resumeSubheading
      {Suzhou Benqio Technology Ltd.}{Suzhou, China}
      {Machine Learning Engineer}{July 2023 \textbf{--} March 2024}
        \resumeItemListStart
            \resumeItem{Designed and wrote a machine learning data pipeline for automatically filtering insurance contracts for MSIG insurance.}
            \resumeItem{Saved hundreds of employees' time to find the most viable contracts.}
            \resumeItem{Implemented the entire pipeline locally to prevent sensitive client data from leaking.}
            \resumeItem{Saved thousands of dollars in deployment by quantizing LLama to lower precision floating point for more efficient inference, reducing memory usage 4x and allowing inference of a 33 billion parameter LLM to run with under 24GB of VRAM in just a single GPU.}
            \resumeItem{Very efficiently fine-tuned LLMs to small custom datasets using LoRA training.}
            \resumeItem{Designed and wrote a custom HTTP server implementing REST APIs handling internal company requests.}
            \resumeItem{Used sentence embeddings and Qdrant as a vector database to index and recall relevant parts of documents for use by LLMs.}
        \resumeItemListEnd

    \resumeSubheading
      {Pinpoint AVL}{Santa Cruz, California}
      {Software Engineer}{October 2022 \textbf{--} June 2023}
        \resumeItemListStart
             \resumeItem{I made GPS tracking for TAPS and Santa Cruz Metro, which tens of thousands of students use for transportation to class.}
             \resumeItem{I integrated Google Maps to track individual metro bus routes' real-time location and capacity, allowing students and faculty to plan their trips more efficiently.}
             \resumeItem{Designed and built a device mounted on buses for tracking location and capacity.}
             \resumeItem{Created data processing pipelines for GTFS feeds and GPS data to optimize transportation routes and detect bottlenecks.}
             \resumeItem{I used Raspberry Pi Picos, Arduinos, and a custom bus driver dashboard connected to the bus power supply with inter-device communication using I2C and UART.}
             \resumeItem{Utilized custom multi-core scheduling in the Raspberry Pi to balance workload between logging to disk, LTE communication, and I2C.}
             \resumeItem{I wrote embedded AArch64 applications and implemented the backend REST API.}
        \resumeItemListEnd
  
    \resumeSubheading
      {AbiTalk, Inc.}{San Jose, California}
      {Software Engineer}{July 2019 \textbf{--} June 2022}
        \resumeItemListStart
            \resumeItem{Developed educational mobile games for kids learning English and speech impediments used by hundreds of school districts.}
            \resumeItem{Implemented GUI, sound design, and statistics gathering for data-driven teaching.}
            \resumeItem{I worked with the Apple ecosystem, Swift programming, music licensing, and publishing for the Apple App Store.}
        \resumeItemListEnd

  \resumeSubHeadingListEnd

\section{Skills}
  \vspace{2pt}
  \resumeSubHeadingListStart
    \small{\item{
        \textbf{Languages:}{ C/C++, Python, CUDA, Javascript/Typescript, Rust, Go, SQL, React, RISC-V Assembly, Haskell, Agda, \LaTeX, Postscript, GLSL} \\ \vspace{3pt}
        \textbf{Technologies:}{ PyTorch, OpenCV, SQLite, PostgreSQL, Webassembly, WebGL, Git, Linux Kernel Modules } \\ \vspace{3pt}
    }}
  \resumeSubHeadingListEnd


\section{Education}
  \vspace{3pt}
  \resumeSubHeadingListStart
    \resumeEducationHeading
      {University of California, Santa Cruz}{Santa Cruz, California}
      {B.S    \textbf{GPA: 3.97/4.00}}{Sep 2022 \textbf{--} Jun 2024}
  \resumeSubHeadingListEnd

\end{document}
